
\begin{otherlanguage}{english}

\vspace*{-4em}

    \begin{center}
        \textbf{Editorial Board}
    \end{center}
    
    
    
    \begin{multicols}{2}
       % \begin{flushleft}
            
        \scriptsize
    
        \begin{center}
        \textbf{Editor-in-Chief}
        \end{center}
    
\noindent\textbf{T. V. Rastimeshina}, Dr. Sci. (Polit.), Assoc. Prof., Professor, RSSU (Moscow)
    
        \begin{center}
        \textbf{Deputy Editor-in-Chief}
        \end{center}
    
\noindent  \textbf{A. I. Pirogov}, Dr. Sci. (Philos.), Prof., Professor, MIET (Moscow)

 \vspace{2em}       
\noindent Yu. P. Aniskin, Dr. Sci. (Econ.), Prof., Chair of Editorial Board; Professor at the Chair of Economics, Management and Finances, National Research University of Electronic Technology

\noindent A. N. Chumakov, Dr. Sci. (Philos.), Prof., Co-Chair of Editorial Board; Professor at the Chair of Geopolicy of Faculty of Global Studies, Lomonosov Moscow State University

\noindent V. S. Agapov, Dr. Sci. (Psy.), Prof., Professor at the Chair of Legal Psychology, Kikot Moscow University of the Ministry of the Interior of Russia

\noindent S. V. Alekseev, Dr. Sci. (Ped.), Prof., Professor at the Chair of Environmental Pedagogy and Human Well-Being, St. Petersburg Academy of Postgraduate Pedagogical Education

\noindent I. Yu. Alekseeva, Dr. Sci. (Philos.), Assoc. Prof., Leading Researcher at the Sector of Philosophical Problems of Social Sciences and Humanities, Institute of Philosophy of the Russian Academy of Sciences

\noindent S. N. Bolshakov, Dr. Sci. (Econ.), Dr. Sci. (Polit.), Prof., Professor at the Department of Political Science and Applied Political Work of the Faculty of Political and Social Sciences, Russian State Social University

\noindent Ya. V. Bondareva, Dr. Sci. (Philos.), Prof., Head of the Chair of Philosophy, State University of Education

\noindent O. V. Brizhak, Dr. Sci. (Econ.), Assoc. Prof., Professor at the Department of Economic Theory, Financial University under the Government of the Russian Federation

\noindent I. P. Gladilina, Dr. Sci. (Ped.), Prof., Professor at the Chair of Financial Management and Finance Law, Moscow City University of Management Moscow Government

\noindent I. S. Gladkov, Dr. Sci. (Econ.), Full Prof., Principal Researcher, Russian Academy of Sciences

\noindent N. D. Guskova, Dr. Sci. (Econ.), Prof., Professor at the Management Department of Economics Institute, National Research Mordovia State University

\noindent A. V. Danilchenko, Dr. Sci. (Econ.), Prof., Dean of the Faculty of Marketing, Management, and Entrepreneurship, Belarusian National Technical University (Minsk, Belarus)

\noindent M. G. Evdokimova, Dr. Sci. (Ped.), Assoc. Prof., Director of the Institute of Linguistic and Pedagogical Education, National Research University of Electronic Technology

\noindent V. G. Egorov, Dr. Sci. (Hist.), Dr. Sci. (Econ.), Prof., Director of Scientific School ``Economic Theory'', Plekhanov Russian University of Economics

\noindent Yu. Ya. Eleneva, Dr. Sci. (Econ.), Prof., Head of the Financial Management Department, Moscow State University of Technology STANKIN

\noindent A. N. Zakhlebnyi, Dr. Sci. (Ped.), Prof., Academician of Russian Academy of Education, Head of the Laboratory of Ecological Education of Institute of Syllabus and Methods of Teaching, Russian Academy of Education

\noindent G. P. Ivanova, Dr. Sci. (Ped.), Prof., Professor at the Chair of Primary Education of the Faculty of Pre-University and Pre-Vocational Education, State University of Education

\noindent V. V. Ilyin, Dr. Sci. (Philos.), Prof., Professor at the Social Sciences Department, Kaluga Branch of Bauman Moscow State Technical University

\noindent Davide Infante, Dr. Sci. (Polit. Econ.), Adjunt Professorat the Department of Economics and Statistics,, University of Calabria (Rende, Italy)

\noindent V. A. Kalney, Dr. Sci. (Ped.), Prof., Head of the Chair of Pedagogy and Psychology, Russian International Academy of Tourism

\noindent G. V. Lobastov, Dr. Sci. (Philos.), Prof., Chairman of the Russian Philosophical Society ``Dialectics and Culture''

\noindent A. I. Loiko, Dr. Sci. (Philos.), Prof., Head of the Department ``Philosophical Teachings'', Belarusian National Technical University (Minsk, Belarus)

\noindent N. M. Mamedov, Dr. Sci. (Philos.), Prof., Professor at the Chair of Information Processes Management of Faculty of Journalism of the Institute of State Service and Administration, Russian Presidential Academy of National Economy and Public Administration

\noindent N. V. Mikhalkin, Dr. Sci. (Philos.), Prof., Head of the Universitywide Department ``Philosophy and Humanities'', Moscow State University of Psychology \& Education

\noindent D. E. Muza, Dr. Sci. (Philos.), Prof., Full Member of the Crimean Academy of Sciences, Head of the Chair of Global and National Culture, Donetsk State University (Donetsk)

\noindent N. N. Ravochkin, Dr. Sci. (Philos.), Assoc. Prof., Professor at the History, Philosophy and Social Sciences Department, Kuzbass State Technical University named after T. F. Gorbachev; Professor at the Educational Technologies Department, Kuzbass State Agrarian University named after V. N. Poletskov

\noindent O. G. Rumba, Dr. Sci. (Ped.), Prof., Professor at the Department of ``Theory and Methodology of Sports, Sports Kinesiology, Wellness and Adaptive Physical Culture'' of the Institute of Sports and Physical Education, M. K. Ammosov North-Eastern Federal University

\noindent T. A. Salimova, Dr. Sci. (Econ.), Prof., Professor at the Quality Management Department of Economics Institute, National Research Mordovia State University

\noindent S. A. Stepanov, Dr. Sci. (Ped.), Prof., Head of N. N. Moiseev Scientific School, International Independent University of Environmental \& Political Sciences

\noindent I. V. Taranova, Dr. Sci. (Econ.), Prof., Professor at the Department of Land Resources and Real Estate Assets Management, State University of Land Use Planning

\noindent A. V. Fahrutdinova, Dr. Sci. (Ped.), Prof., Head of the Department of Foreign Languages in International Relations of the Higher School of Foreign Languages and Translation Studies, Kazan Federal University

\noindent T. I. Shukshina, Dr. Sci. (Ped.), Prof., Member of Expert Council of RF Higher Attestation Commission (online), Vice Rector for Research of Mordovian State Pedagogical University named after M. E. Evseviev, Head of Mordovian Scientific Center of the Russian Academy of Education

\noindent K. V. Yakushenko, Dr. Sci. (Econ.), Assoc. Prof., Vice-Principal for Research, Belarusian National Technical University (Minsk, Belarus)
  %  \end{flushleft}    
    \end{multicols}

\begin{flushleft}
\footnotesize
ESGI is a peer-reviewed scholarly journal registered by the Federal Agency on Press and Mass Communications
of the Russian Federation on March 24, 2017.

\vspace{1em}
\textbf{Founder and publisher}: National Research University of Electronic Technology (MIET), 124498, Moscow,
Zelenograd, Shokin square, Bld. 1.
\end{flushleft}

\noindent
\begin{minipage}[t]{.48\textwidth}
    
\begin{flushleft}
  \footnotesize
        Managing editor — \textbf{A. I. Pirogov}\\
Science editor — \textbf{T. V. Rastimeshina} \\
Executive editor — \textbf{Yu. V. Lunkina }\\
Digital typesetting — \textbf{S. O. Brylev}
    \end{flushleft}
\end{minipage}\hspace{0.04\textwidth}
\begin{minipage}[t]{.48\textwidth}
    \begin{flushleft}
        \footnotesize
        Senior editor — \textbf{T. V. Rastimeshina}\\
        Editors — \textbf{E. V. Malinkina, A. V. Lobanova}\\
        Cover designer — \textbf{S. Yu. Ryzhkov}
    \end{flushleft}
\end{minipage}

\begin{flushleft}
    \footnotesize
    \textbf{Address}: Russia, 124498, Moscow, Zelenograd, Shokin square, Bld. 1, MIET.\\
    \textbf{Тел}.: +7-499-729-76-02\\
    \textbf{Е-mail}: \href{mailto:esgi.miet@yandex.ru}{esgi.miet@yandex.ru} \hspace{3em}
    \textbf{Web}: \url{http://esgi-miet.ru}

     \vspace{1em}
    Signed to print \esgiPDate. Sheet size 60\(×\)84 1/8. Digital printing.\\
    Conventional printed sheets: \esgiUPL{}. Published sheets: \esgiUIL{}. Order No.~\esgiPRN{}.\\
    Printed at MIET printing workshop: 124498, Moscow, Zelenograd, Shokin square, Bld. 1, MIET.
\end{flushleft}

\end{otherlanguage}

\normalsize
\setmainlinespread
